Sperm should evolve to make female meiosis fair.

### 2014-07-27 writeup_and_notes/GeneticsResub/reviews.tex
yb (nearly) finalized changes for resub

\begin{document}
Please find attached a new manuscript for your evaluation for publication in GENETICS, titled  `Sperm should evolve to make female meiosis fair.' 
The positive and constructive reviews of our previous submission with the same title (\emph{MS ID\#: GENETICS/2014/167064})  where extremely useful in our crafting of this revision. 
Below we discuss how this paper was improved by addressing, in detail, previous concerns \emph{point-by-point}, but first we address the major  concerns with our previous submission.
\begin{itemize}
\begin{singlespace}
\item \emph{{\bf{Major concern 1 -- }} The paper as written establishes that factors expressed in sperm should generally evolve to suppress drivers of meiotic drive in female meiosis. However, as Reviewer 1 points out, this is different from showing that factors expressed in females should evolve to delay completion of meiosis until after fertilization. There is general agreement that the argument needs to be completed so that it supports all conclusions and that the justification for study of the question be improved. Reviewer 2 has provided many valuable suggestions along these lines.}  \newline \\
{\bf{Response -- }} \gc{We thank the reviewers and editor for highlighting
this point. In this revision we make it clear} that our primary
argument is that, given a chance to influence female meiosis, sperm
will evolve to increase its fairness (as reflected in our title), {\it
  and not} that females should delay the completion of meiosis so as to recruit help from sperm in making meiosis fair (as could have been interpreted from our previous draft). 
\end{singlespace}

\begin{singlespace}
\item \emph{{\bf{Major concern 2 -- }} The format of this submission departs from the style of GENETICS (model description and analysis, literature citations, etc.). As a result, it is unclear whether GENETICS is the appropriate or even the intended forum for this work.} \newline \\
{\bf{Response -- }}  We believe our manuscript presents 
(1) a rigorous and theoretical model, and 
(2) research questions that can be addressed by molecular genetics,
transmission genetics, studies of genome structure, phylogenetics and
population genetics. As such, GENETICS is a particularly appropriate
venue for our paper.  Our view is echoed by comments from Reviewer 2 who stated  `Overall I found the paper to be well written and organized, and because of this, the theory that the authors describe will be accessible to a broad spectrum of the readership of Genetics not just other theoreticians.'
The suitability of the topic of our manuscript is clear from our reference list -- a strong plurality (over 25\%) of our works cited appeared in GENETICS, placing our work squarely within the tradition of GENETICS papers.
\gc{We apologize for the formatting issues. We have corrected these
  issues, and included a short METHODS section to introduce our models.} \\
\end{singlespace} 
\end{itemize}
We thank you for your previous comments and for consideration of this revised manuscript. 
To aid in your consideration, we provide \gc{the previous reviews and a
detailed response below. }
\\
\\
Sincerely,  \\
Yaniv Brandvain and Graham Coop.

@@

\begin{singlespace}
{\bf{Response -- }} We thank the reviewer for this comment, and have reworked our manuscript to focus 
	around our major result -- that sperm are expected to evolve to prevent female meiotic drive. 
	We completely agree that this delay \gc{cannot} be favored by ``evolutionary foresight'' and have 
	modified our manuscript to ensure that readers do not
        interpret our argument in this way. \gc{We have now added
          significantly to our  revised introduction and discussion to
          clarify this point. 	
We also now more explicitly refer readers to a discussion of
        hypotheses proposed to explain female meiotic arrest (Mira
        '98), so that our discussion can be seen as being distinct
        from that. }

@@

\begin{singlespace}
	{\bf{Response -- }}  \gc{We believe that this is an important
        phenomenon. We have strengthened our discussion of this point
        throughout the introduction,
        we have also highlighted the points raised by R2 about 
        the evidence of pervassive female drive and the opportunities for
        sperm-based products
        to interfer with female meiosis.
	We have modified the manuscript to clarify that it is quite impressive that there is evidence
	for male influence on female drive at both of the two described
        female meiotic drive elements in animals. 
	We note that although direct evidence for polymorphic female meiotic drive
        in animals is modest (i.e. these two loci in mice), 
	this likely reflects the fact that it is very hard to study
        outside of model organisms. 
Given the increasing tractibility of genetics in many traditionally
        non-model systems, and the growing awareness of the importance
        of genetic conflicts in shaping molecular systems, we think
        that it is timely to offer a framework to understand one
        aspect of sperm-egg 
        interactions and provide
strong predictions that could guide analyses.}
\end{singlespace}
\end{enumerate}

>>>>

\begin{document}
Please find attached a new manuscript for your evaluation for publication in GENETICS, titled  `Sperm should evolve to make female meiosis fair.' 
The positive and constructive reviews of our previous submission with the same title (\emph{MS ID\#: GENETICS/2014/167064})  where extremely useful in our crafting of this revision. 
Below we discuss how this paper was improved by addressing, in detail, previous concerns \emph{point-by-point}, but first we address the major  concerns with our previous submission.
\begin{itemize}
\begin{singlespace}
\item \emph{{\bf{Major concern 1 -- }} The paper as written establishes that factors expressed in sperm should generally evolve to suppress drivers of meiotic drive in female meiosis. However, as Reviewer 1 points out, this is different from showing that factors expressed in females should evolve to delay completion of meiosis until after fertilization. There is general agreement that the argument needs to be completed so that it supports all conclusions and that the justification for study of the question be improved. Reviewer 2 has provided many valuable suggestions along these lines.}  \newline \\
{\bf{Response -- }} We thank the reviewers and editor for highlighting
this point. In this revision we make it clear that our primary
argument is that, given a chance to influence female meiosis, sperm
will evolve to increase its fairness (as reflected in our title), {\it
  and not} that females should delay the completion of meiosis so as to recruit help from sperm in making meiosis fair (as could have been interpreted from our previous draft). 
\end{singlespace}

\begin{singlespace}
\item \emph{{\bf{Major concern 2 -- }} The format of this submission departs from the style of GENETICS (model description and analysis, literature citations, etc.). As a result, it is unclear whether GENETICS is the appropriate or even the intended forum for this work.} \newline \\
{\bf{Response -- }}  We believe our manuscript presents 
(1) a rigorous and theoretical model, and 
(2) research questions that can be addressed by molecular genetics,
transmission genetics, studies of genome structure, phylogenetics and
population genetics. As such, GENETICS is a particularly appropriate
venue for our paper.  Our view is echoed by comments from Reviewer 2 who stated  `Overall I found the paper to be well written and organized, and because of this, the theory that the authors describe will be accessible to a broad spectrum of the readership of Genetics not just other theoreticians.'
The suitability of the topic of our manuscript is clear from our reference list -- a strong plurality (over 25\%) of our works cited appeared in GENETICS, placing our work squarely within the tradition of GENETICS papers.
We apologize for the formatting issues. We have corrected these
  issues, and included a short METHODS section to introduce our models. \\
\end{singlespace} 
\end{itemize}
We thank you for your previous comments and for consideration of this revised manuscript. 
To aid in your consideration, we provide the previous reviews and a
detailed response below. 
\\
\\
Sincerely,  \\
Yaniv Brandvain and Graham Coop.

@@

\begin{singlespace}
{\bf{Response -- }} We thank the reviewer for this comment, and have reworked our manuscript to focus 
	around our major result -- that sperm are expected to evolve to prevent female meiotic drive. 
	We completely agree that this delay cannot be favored by ``evolutionary foresight'' and have 
	modified our manuscript to ensure that readers do not
        interpret our argument in this way. We have now added
          significantly to our  revised introduction and discussion to
          clarify this point. 	
We also now more explicitly refer readers to a discussion of
        hypotheses proposed to explain female meiotic arrest (Mira
        '98), so that our discussion can be seen as being distinct
        from that.

@@

\begin{singlespace}
	{\bf{Response -- }}  We believe that this is an important
        phenomenon. We have strengthened our discussion of this point
        throughout the introduction,
        we have also highlighted the points raised by R2 about 
        the evidence of pervasive female drive and the opportunities for
        sperm-based products
        to interfere with female meiosis.
	We have modified the manuscript to clarify that it is quite impressive that there is evidence
	for male influence on female drive at both of the two described
        female meiotic drive elements in animals. 
	We note that although direct evidence for polymorphic female meiotic drive
        in animals is modest (i.e. these two loci in mice), 
	this likely reflects the fact that it is very hard to study
        outside of model organisms. 
Given the increasing tractability of genetics in many traditionally
        non-model systems, and the growing awareness of the importance
        of genetic conflicts in shaping molecular systems, we think
        that it is timely to offer a framework to understand one
        aspect of sperm-egg 
        interactions and provide
strong predictions that could guide analyses.
\end{singlespace}
\end{enumerate}
